---
title: "Effect of Covid on marriage licenses"
author: 
  - 'Chris Yong Hong Sen'
date: today
date-format: long
abstract: "..."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r loading packages and reading data}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)

data <- read_csv('../data/analysis_data/analysis_data.csv')
```


# Introduction

We used @talia, @opendatatoronto, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection


# Data {#sec-mydatasection}

Some of our data is of marriage licenses (@fig-marriage), from @palmerpenguins.

```{r graph for visualisaiton}

data %>%
  ggplot(aes(x = time_period, y = marriage_licenses)) +
  geom_point(aes(col = civic_centre)) +
  theme_minimal() +
  ggtitle('Number of Marriage Licenses Across Time')

min(data$time_period)
max(data$time_period)
```

# Discussion

## First discussion point {#sec-first-point}
Overall,  we can see that from 2020 to 2021, marriage licenses given across all districts have decreased, with marriage licenses from civic district Toronto showing a more conspicuous decrease. 

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References

